---
title: "Weight of Fish"
author: "Your Name"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```



# Predicting Fish Weight

```{r}

pwt = lm(Weight~ Length1+ Length2+ Length3 + Height,data=Perch)
summary(pwt)
```
## Perch

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

Our best model is 4(1) because it fills the most categories filled.

### Best Two regressor model

the best model you can get using 2 models is length3 and height

## Pike

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Pike)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

Our best model is 4(1) because it fills the most categories filled.

### Best Two regressor model

the best model you can get using 2 models is length1 and length3

## Roach

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

Our best model is 4(1) because it fills the most categories filled.

### Best Two regressor model

the best model you can get using 2 models is length1 and length3

## Final Summary Statements

The best model at all times is 4(1) and the best 2 regresser for perch,pike and roach are length3 and height, length1 and length 3, and length1 and length 3 respectively.